Revision Plan for SIGCOMM'24 Paper \#293

### 2024-05-21 revision_plan.tex
D1

\noindent\textcolor{blue}{\textbf{Response D.1}
}

>>>>

\noindent\textcolor{blue}{\textbf{Response D.1}
DCTCP is widely deployed and used as the default congestion control algorithm in linux kernel for many years.
Therefore, DCTCP has fewer barriers to adoption and a broader reach compared to other transport protocols.
Moreover, through experiments, we have already demonstrated that DCTCP achieves performance comparable to state-of-the-art proactive transport protocols when utilizing spare bandwidth.
Please see Section 2.3 for more details.
These support PPT to design based on DCTCP.
}
